DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-25 scnn.tex
typo
edits to subspace correspondence

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{figure_architecture_v3}
	\caption{Overall NN architecture, showing here three convolutional layers acting as feature extractors followed by three fully connected layers with softmax acting as the classifier.
    A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
	While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted.
	In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph.
	Graphs are versatile data structures which can model any sampling, even irregular or partial.
	Second, we propose to exploit a hierarchical pixelization of the sphere for the down-sampling operation.
	It allows the NN to analyze the data at multiple scales while preserving the spatial localization of features.
	This figure shows a aetwork that operates on the whole sphere.
	The process is the same when working with partial observations, except that the graph is only built for the region of interest.}
	\label{fig:architecture}
\end{figure*}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors_v2}
	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
		The correspondance is computed in two steps. (i) We compute the PSD of each graph eigenvector.
		(ii) As, for each harmonic index $\ell$, there is $2\ell+1$ spherical harmonics, we sum the contribution of the corresponding $2\ell+1$ graph eigenvectors.
		% No real convergence with increasing Nside.
		% Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
		% (\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
		% The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
		The matrix should ideally be the identity.
		While not the case, the plot shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, while the Fourier modes leak towards adjacent frequency bands in the high frequencies.
		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
		\label{fig:subspace_harmonics_eigenvectors}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{figure_architecture_v3}
	\caption{Overall NN architecture, showing here three convolutional layers acting as feature extractors followed by three fully connected layers with softmax acting as the classifier.
    A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
	While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted.
	In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph.
	Graphs are versatile data structures which can model any sampling, even irregular or partial.
	Second, we propose to exploit a hierarchical pixelization of the sphere for the down-sampling operation.
	It allows the NN to analyze the data at multiple scales while preserving the spatial localization of features.
	This figure shows a network that operates on the whole sphere.
	The process is the same when working with partial observations, except that the graph is only built for the region of interest.}
	\label{fig:architecture}
\end{figure*}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors_v2}
	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
		%The correspondence is computed in two steps.
		First, we compute the power spectral density (PSD) of each graph eigenvector.
		Second, as there is $2\ell+1$ spherical harmonics for each harmonic index $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
		% No real convergence with increasing Nside.
		% Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
		% (\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
		% The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
		The matrix shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
		\label{fig:subspace_harmonics_eigenvectors}
\end{figure}
